Live Functional Programming with Typed Holes

### 2018-04-11 calculus.tex
reword cite sentence and reinsert
fix typo

For the sake of exposition, \HazelnutLive includes ``half-annotated'' lambdas, $\halam{x}{\htau}{\hexp}$, in addition to the unannotated lambdas, $\hlam{x}{\hexp}$, from \Hazelnut.
%
Half-annotated lambdas may appear in synthetic position according to Rule {SLam}, which is standard \cite{Chlipala:2005da}.
%
Unannotated lambdas may only appear where the expected type is known to be either an arrow type or the hole type, which is treated as if it were $\tarr{\tehole}{\tehole}$.
%
To avoid the need for two separate rules, Rule {ALam} uses the auxiliary relation $\arrmatch{\htau}{\tarr{\htau_1}{\htau_2}}$ in \Figref{fig:arrmatch}, which produces the matched arrow type $\tarr{\tehole}{\tehole}$ given the hole type, and operates as the identity on arrow types \cite{DBLP:conf/snapl/SiekVCB15,DBLP:conf/popl/GarciaC15}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% To Cyrus from Matt:
%
% Why say the following here? --- It's discussing a different design that we didn't pursue here.  We should move such discussion to related work.
%
%Note that a system supporting ML-style type reconstruction \cite{damas1982principal} might include a synthetic rule for unannotated lambdas, e.g. as outlined by \citet{DBLP:conf/icfp/DunfieldK13}.
%%

@@

Each well-typed external expression~$e$ expands to a well-typed internal expression~$d$, for evaluation.
%
\Figref{fig:expansion} gives the rules governing expansion, and \Figref{fig:hasType} gives the rules governing type assignment for internal expressions.
%
\Figref{sec:evaluation} discusses internal expression evaluation.

>>>>

For the sake of exposition, \HazelnutLive includes ``half-annotated'' lambdas, $\halam{x}{\htau}{\hexp}$, in addition to the unannotated lambdas, $\hlam{x}{\hexp}$, from \Hazelnut.
%
Half-annotated lambdas may appear in synthetic position according to Rule {SLam}, which is standard \cite{Chlipala:2005da}.
%
Unannotated lambdas may only appear where the expected type is known to be either an arrow type or the hole type, which is treated as if it were $\tarr{\tehole}{\tehole}$.
%
To avoid the need for two separate rules, Rule {ALam} uses the auxiliary relation $\arrmatch{\htau}{\tarr{\htau_1}{\htau_2}}$ in \Figref{fig:arrmatch}, which produces the matched arrow type $\tarr{\tehole}{\tehole}$ given the hole type, and operates as the identity on arrow types \cite{DBLP:conf/snapl/SiekVCB15,DBLP:conf/popl/GarciaC15}.
%
\Secref{sec:related} dicusses how \HazelnutLive might be enriched with
with ML-style type reconstruction~\cite{damas1982principal}, perhaps via
the approach outlined by~\citet{DBLP:conf/icfp/DunfieldK13}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% To Cyrus from Matt:
%
% Why say the following here? --- It's discussing a different design that we didn't pursue here.  We should move such discussion to related work.
%
%Note that a system supporting ML-style type reconstruction \cite{damas1982principal} might include a synthetic rule for unannotated lambdas, e.g. as outlined by \citet{DBLP:conf/icfp/DunfieldK13}.
%%

@@

Each well-typed external expression~$e$ expands to a well-typed internal expression~$d$, for evaluation.
%
\Figref{fig:expansion} gives the rules governing expansion, and \Figref{fig:hasType} gives the rules governing type assignment for internal expressions.
%
\Secref{sec:evaluation} discusses internal expression evaluation.
